Descriptive analysis

### 2021-04-02 analysis/01_data-overview.Rmd
Run all models and predictions!

  tar_load(panel_done_trimmed)
})
```

@@

We have `r panel_done_trimmed %>% distinct(gwcode) %>% nrow()` countries in this data, spanning `r panel_done_trimmed %>% distinct(year) %>% nrow()` possible years. Here's a lookup table of all the countries included:

@@

- **Civil society stuff**
  - CSO entry and exit: `v2cseeorgs`
  - CSO repression: `v2csreprss`
  - CSO consultation: `v2cscnsult`
  - CSO participatory environment: `v2csprtcpt`
  - CSO women's participation: `v2csgender`
  - CSO anti-system movements: `v2csantimv`
  - Core civil society index (entry/exit, repression, participatory env): `v2xcs_ccsi`
- **Freedom of expression stuff**
  - Freedom of expression index: `v2x_freexp`
  - Freedom of expression and alternative sources of information index: `v2x_freexp_altinf`
  - Freedom of academic and cultural expression: `v2clacfree`
  - Media self-censorship: `v2meslfcen`
- **Repression stuff**
  - Religious organization repression: `v2csrlgrep`
  - Govt censorship effort - media: `v2mecenefm`
  - Harassment of journalists: `v2meharjrn`
- **Rights indexes**
  - Civil liberties index: `v2x_civlib`
  - Physical violence index: `v2x_clphy`
  - Private civil liberties index: `v2x_clpriv`
  - Political civil liberties index: `v2x_clpol`
- **Democracy**
  - Polyarchy index: `v2x_polyarchy`
  - Regimes of the world category: `v2x_regime_amb`

@@

```{r glimpse-combined}
glimpse(panel_done_trimmed)
```

@@

```{r show-country-years-summary}
panel_done_trimmed %>% 
  summarize(`Number of countries` = length(unique(gwcode)),
            `Number of years` = length(unique(year)),
            `First year` = min(year),
            `Last year` = max(year)) %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

@@

```{r show-country-year-count}
panel_done_trimmed %>% 
  count(Year = year, name = "Number of countries") %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

@@

```{r plot-missing}
panel_done_trimmed %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

@@

```{r show-missing-rows, class.source="fold-show"}
panel_done_trimmed %>% 
  filter(is.na(advocacy)) %>% 
  select(gwcode, year, country, iso3, advocacy, entry, funding)
```

@@

```{r show-missing-pts, class.source="fold-show"}
panel_done_trimmed %>% 
  filter(is.na(PTS)) %>% 
  select(gwcode, year, country, iso3, PTS, PTS_factor)
```

@@

```{r plot-missing-laws}
panel_done_trimmed %>% 
  filter(laws) %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

>>>>

  tar_load(panel)
})
```

@@

We have `r panel %>% distinct(gwcode) %>% nrow()` countries in this data, spanning `r panel %>% distinct(year) %>% nrow()` possible years. Here's a lookup table of all the countries included:

@@

- **Civil society stuff**
  - CSO entry and exit: `v2cseeorgs`
  - CSO repression: `v2csreprss`
  - CSO consultation: `v2cscnsult`
  - CSO participatory environment: `v2csprtcpt`
  - CSO women's participation: `v2csgender`
  - CSO anti-system movements: `v2csantimv`
  - Core civil society index (entry/exit, repression, participatory env): `v2xcs_ccsi`
- **Freedom of expression stuff**
  - Freedom of expression index: `v2x_freexp`
  - Freedom of expression and alternative sources of information index: `v2x_freexp_altinf`
  - Freedom of academic and cultural expression: `v2clacfree`
  - Media self-censorship: `v2meslfcen`
- **Repression stuff**
  - Religious organization repression: `v2csrlgrep`
  - Govt censorship effort - media: `v2mecenefm`
  - Harassment of journalists: `v2meharjrn`
- **Rights indexes**
  - Civil liberties index: `v2x_civlib`
  - Physical violence index: `v2x_clphy`
  - Private civil liberties index: `v2x_clpriv`
  - Political civil liberties index: `v2x_clpol`
- **Democracy and governance stuff**
  - Polyarchy index (for electoral democracies): `v2x_polyarchy`
  - Liberal democracy index (for democracies in general): `v2x_libdem`
  - Regimes of the world category: `v2x_regime`
  - Political corruption index: `v2x_corr` (less to more, 0-1) (public sector + executive + legislative + judicial corruption)
  - Rule of law index: `v2x_rule`

@@

```{r glimpse-combined}
glimpse(panel)
```

@@

```{r show-country-years-summary}
panel %>% 
  summarize(`Number of countries` = length(unique(gwcode)),
            `Number of years` = length(unique(year)),
            `First year` = min(year),
            `Last year` = max(year)) %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

@@

```{r show-country-year-count}
panel %>% 
  count(Year = year, name = "Number of countries") %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

@@

```{r plot-missing}
panel %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

@@

```{r show-missing-rows, class.source="fold-show"}
panel %>% 
  filter(is.na(advocacy)) %>% 
  select(gwcode, year, country, iso3, advocacy, entry, funding)
```

@@

```{r show-missing-pts, class.source="fold-show"}
panel %>% 
  filter(is.na(PTS)) %>% 
  select(gwcode, year, country, iso3, PTS, PTS_factor)
```

@@

```{r plot-missing-laws}
panel %>% 
  filter(laws) %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

### 2021-04-02 analysis/02_descriptive-analysis.Rmd
Run all models and predictions!

  canary <- tar_read(panel_done_trimmed)
  tar_load(world_map)
})
```

@@

```{r make-map-data}
things_to_map <- canary %>% 
  filter(year %in% c(2000, 2014)) %>% 
  select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
  pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
  mutate(new_laws = barriers_total_2014 - barriers_total_2000,
         new_laws = ifelse(new_laws <= 0, 0, new_laws),
         new_laws = ceiling(new_laws)) %>% 
  mutate(diff_csrepress = v2csreprss_2014 - v2csreprss_2000,
         diff_csrepress_trunc = case_when(
           diff_csrepress >= 2 ~ 2,
           diff_csrepress <= -2 ~ -2,
           TRUE ~ diff_csrepress
         )) %>% 
  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_2000,
         pct_change_csrepress_trunc = case_when(
           pct_change_csrepress >= 5 ~ 5,
           pct_change_csrepress <= -5 ~ -5,
           TRUE ~ pct_change_csrepress
         ))

@@

```{r map-ngo-laws}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

@@

```{r map-cs-repression}
map_cs_repression <- ggplot() +
  geom_sf(data = map_data, aes(fill = diff_csrepress_trunc),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_scico(palette = "vik", direction = -1,
                   limits = c(-1, 1) * max(abs(map_data$diff_csrepress_trunc), na.rm = TRUE),
                   breaks = seq(-4, 4, 1), na.value = "grey80") +
  guides(fill = guide_colorbar(reverse = TRUE, ticks = FALSE,
                               barwidth = unit(7, units = "lines"),
                               barheight = unit(0.5, units = "lines"))) +
  labs(fill = "Change in V-Dem civil society repression between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(12, "lines"),
                                              padding = margin(r = 10)))
map_cs_repression
```

@@

# Civil society restrictions and other kinds of repression

```{r repression-matrix, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
library(GGally)
repression_only <- canary %>% 
  filter(year == 2014) %>% 
  select(barriers_total, PTS, gh_alljourn, 
         v2clacfree, v2csrlgrep, v2mecenefm, v2meharjrn, v2meslfcen,
         v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)

ggscatmat(repression_only, alpha = 0.4) + 
  theme_ngo(base_size = 6)
```

>>>>

  canary <- tar_read(panel)
  tar_load(world_map)
})
```

@@

```{r make-map-data}
things_to_map <- canary %>% 
  filter(year %in% c(1990, 2013)) %>% 
  select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
  pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
  mutate(new_laws = barriers_total_2013 - barriers_total_1990,
         new_laws = ifelse(new_laws <= 0, 0, new_laws),
         new_laws = ceiling(new_laws)) %>% 
  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1990,
         diff_csrepress_trunc = case_when(
           diff_csrepress >= 2 ~ 2,
           diff_csrepress <= -2 ~ -2,
           TRUE ~ diff_csrepress
         )) %>% 
  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1990,
         pct_change_csrepress_trunc = case_when(
           pct_change_csrepress >= 5 ~ 5,
           pct_change_csrepress <= -5 ~ -5,
           TRUE ~ pct_change_csrepress
         ))

@@

```{r map-ngo-laws}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 8)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 1990 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

@@

```{r map-cs-repression}
map_cs_repression <- ggplot() +
  geom_sf(data = map_data, aes(fill = diff_csrepress_trunc),
          color = "black", size = 0.1) +
  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
  scale_fill_scico(palette = "vik", direction = -1,
                   limits = c(-1, 1) * max(abs(map_data$diff_csrepress_trunc), na.rm = TRUE),
                   breaks = seq(-4, 4, 1), na.value = "grey80") +
  guides(fill = guide_colorbar(reverse = FALSE, ticks = FALSE,
                               barwidth = unit(7, units = "lines"),
                               barheight = unit(0.5, units = "lines"))) +
  labs(fill = "Change in V-Dem civil society repression between 1990 and 2013") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(12, "lines"),
                                              padding = margin(r = 10)))
map_cs_repression
```

@@
